\chapter*{BOARD OF EXAMINATION AND \\ CERTIFICATE OF APPROVAL}
\addcontentsline{toc}{chapter}{\normalfont Board of Examination and Certificate of Approval}
This project work (PRO-406) entitled ``\textbf{A Comparative Data Analysis of Gravitational Wave Signals From Binary Stars Coalescence of GW170817, GW190521, and GW190814}” by Shivaji Chaulagain, Symbol No. 502820050, T.U. Registration No. 5-2-282-86-2019 under the supervision of Dr. Shreeram Nagarkoti in the Department of Physics, St. Xavier's College, Maitighar, Institute of Science and Technology (IoST), Tribhuvan University (T.U.), is hereby submitted for the partial fulfillment of the Bachelor of Science (B.Sc.) degree in Physics. This report has been accepted and forwarded to the Controller of Examination, Institute of Science and Technology, Tribhuvan University, Nepal for the legal procedure.

\vspace{50pt}
\begin{multicols}{2}
	\begin{flushleft}
		\underline{\hspace{5.3cm}} \\
		\textbf{Dr. Shreeram Nagarkoti} \\
		\textbf{Supervisor} \\
		Department: Physics \\
		Institute: St. Xavier's College, Maitighar \\
		University: Tribhuvan University
	\end{flushleft}
	
	\begin{flushleft}
		\vspace{30pt}
		\underline{\hspace{5.3cm}} \\
		% \underline{\hspace{5.3cm}} \\
		\textbf{Internal Examiner} \\
		Department: Physics \\
		Campus/Institute:  \\
		University: Tribhuvan University
	\end{flushleft}
	

	
	\columnbreak
	\begin{flushright}
		\vspace{30pt}
		\underline{\hspace{5.3cm}} \\
		% \underline{\hspace{5.3cm}} \\
		\textbf{External Examiner} \\
		Department: Physics \\
		Campus/Institute:\underline{\hspace{4cm}}  \\
		University: Tribhuvan University
	\end{flushright}
	
	\begin{flushright}
		\vspace{30pt}
		\underline{\hspace{5.3cm}} \\
		\textbf{Dr. Binod Adhikari} \\
		\textbf{Head of Department} \\
		Department of Physics \\
		St. Xavier's College, Maitighar\\
		Tribhuvan University
	\end{flushright}


	
	
	
	
	
\end{multicols}


\vspace{80pt}
\begin{center}
{\fontsize{16}{12}\selectfont \textbf{10, September, 2024}}
\end{center}



                                              